Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-11 paper.tex
update code

\begin{lstlisting}
case class VS(vals: Set[Storable], time: Time, store: BStore)
type MCont = VS => VS
type Cont  = MCont => (VS => VS)

def aval(e: Expr, env: Env, store: BStore, time: Time, cont: Cont, rcont: MCont): VS = {
  val new_time = (e::time).take(k)

  e match {
    case Let(x, App(f, ae), e) =>
      val closures = atomicEval(f, env, store).toList.asInstanceOf[List[Clos]]

      def ndCont(closures: List[Clos])(r: MCont)(vs: VS): VS = {
        closures match {
          case Nil => r(vs)
          case Clos(Lam(v, body), c_env)::rest =>
            val baddr = allocBind(v, vs.time)
            val new_env = c_env + (v -> baddr)
            val new_store = vs.store.update(baddr, atomicEval(ae, env, vs.store))
            aval(body, new_env, new_store, new_time, ndCont(rest), (vs1: VS) => {
                    r(VS(vs.vals ++ vs1.vals, vs1.time, vs1.store))
                  })
        }
      }
      def mtCont(vs: VS): VS = {
        val baddr = allocBind(x, vs.time)
        val new_env = env + (x -> baddr)
        val new_store = vs.store.update(baddr, vs.vals)
        aval(e, new_env, new_store, vs.time, cont, rcont)
      }

      ndCont(closures)(mtCont)(VS(Set(), new_time, store))

    case ae if isAtomic(ae) =>
      val ds = atomicEval(ae, env, store)
      cont(rcont)(VS(ds, new_time, store))
  }
}

def analyze(e: Expr) = aval(e, Map(),
                            Store[BAddr, Storable](Map()),
                            List(),
                            (r: MCont) => (vs: VS) => vs,
                            (vs: VS) => vs)

\end{lstlisting}

>>>>

\begin{lstlisting}
case class VS(vals: Set[Storable], time: Time, store: BStore)

type MCont = VS => Set[VS]
type Cont  = MCont => (VS => Set[VS])

def aval(e: Expr, env: Env, store: BStore, time: Time, cont: Cont, rcont: MCont): Set[VS] = {
  val new_time = (e::time).take(k)
  e match {
    case Let(x, App(f, ae), e) =>
      val closures = aeval(f, env, store).toList.asInstanceOf[List[Clos]]

      def nd(closures: List[Clos]): Set[VS] = {
        val Clos(Lam(v, body), c_env)::rest = closures
        val baddr = allocBind(v, new_time)
        val new_env = c_env + (v -> baddr)
        val new_store = store.update(baddr, aeval(ae, env, store))
        val new_cont = (r: MCont) => (vs: VS) => {
          val baddr = allocBind(x, vs.time)
          val new_env = env + (x -> baddr)
          val new_store = vs.store.update(baddr, vs.vals)
          aval(e, new_env, new_store, vs.time, cont, r)
        }
        val new_rcont = if (rest.isEmpty) {
          rcont 
        } else (vs: VS) => {
          nd(rest) + vs
        }
        aval(body, new_env, new_store, new_time, new_cont, new_rcont)
      }

      nd(closures)

    case ae if isAtomic(ae) =>
      val ds = aeval(ae, env, store)
      cont(rcont)(VS(ds, new_time, store))
  }
}

def analyze(e: Expr) = aval(e, Map(),
                            Store[BAddr, Storable](Map()), List(),
                            (r: MCont) => (vs: VS) =>  r(vs),
                            (vs: VS) => Set(vs))
\end{lstlisting}
